A large-scale analysis of racial disparities in police stops across the

### 2019-06-27 lib/paper_results.Rmd
progress

pfs <- readRDS(here::here("results", "prima_facie_stats.rds"))
vod <- readRDS(here::here("results", "veil_of_darkness.rds"))
disp <- readRDS(here::here("results", "disparity.rds"))
mj <- readRDS(here::here("results", "marijuana_legalization_analysis.rds"))
```

>>>>

pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```
